---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures"
)
```

# R package `AEenrich`

`r badger::badge_devel("umich-biostatistics/AEenrich", "blue")` `r badger::badge_code_size("umich-biostatistics/AEenrich")`


## Overview

Gene enrichment tests to perform adverse event (AE) enrichment analysis. Unlike the continuous gene expression data, AE data are counts. Therefore, AE data has many zeros and ties. We propose two enrichment tests. One is a modified Fisher's exact test based on pre-selected significant AEs, while the other is based on a modified Kolmogorov-Smirnov statistic.

## Installation

If the devtools package is not yet installed, install it first:

```{r, eval=FALSE}
install.packages('devtools')
```

Then run: 

```{r, eval = FALSE}
# install AEenrich from Github:
devtools::install_github('umich-biostatistics/AEenrich') 
library(AEenrich)
```

## Example usage

### Quick example: 

```{r, eval = FALSE}
##---Experiment 1 
drug.case = 'FLUN'
drug.control = 'FLU'

# AEKS
## Data Type 1
KS_result1 = enrich(df = flu1, dd.group = group, drug.case = drug.case, 
                    drug.control = drug.control, method = 'aeks', n_iter = 1000)
## Data Type 2
KS_result2 = enrich(df = flu2, dd.group = group, drug.case = drug.case, 
                    drug.control = drug.control, method = 'aeks', n_iter = 1000)

# AEFisher
## Data Type 1
fisher_result1 = enrich(df = flu1, dd.group = group, drug.case = drug.case, 
                        drug.control = drug.control, method = 'aefisher', 
                        n_iter = 1000, q.cut = 0.1, or.cut=1.5)
## Data Type 2
fisher_result2 = enrich(df = flu2, dd.group = group, drug.case = drug.case, 
                        drug.control = drug.control, method = 'aefisher', 
                        n_iter = 1000, q.cut = 0.1, or.cut=1.5)
```

### Current Suggested Citation

Li, S. and Zhao, L. (2020). Adverse event enrichment tests using VAERS. arXiv:2007.02266 stat. online Available at: https://arxiv.org/abs/2007.02266 Accessed 7 Jul. 2020.

